Constructing a universe for the setoid model

### 2020-07-06 paper.tex
Phrasing.

Another question regards the relationship between SeTT \cite{mpc19} and XTT
\cite{xtt}. Both systems are syntactic representations of the setoid model with
similar design choices, like definitional proof-irrelevance. We would like to
know whether their respective notions of models are equivalent, that is, whether
we can obtain an XTT model from a SeTT model, and vice versa. Since XTT
universes support universe induction, it is possible that we would need to
extend our own universe with the same principle (see discussion in
Section~\ref{sec:setoid-model} and the previous paragraph). A further question is
whether this mapping of models is functorial.

>>>>

Another question regards the relationship between SeTT \cite{mpc19} and XTT
\cite{xtt}. Both systems are syntactic representations of the setoid model with
similar design choices, like definitional proof-irrelevance. We would like to
know whether their respective notions of models are equivalent.
In particular, we would like to obtain an XTT model from a SeTT model, and vice versa. Since XTT
universes support universe induction, for one direction we would need to
extend our own universe with the same principle (see discussion in
Section~\ref{sec:setoid-model} and the previous paragraph). A further question is
whether this mapping of models is functorial.
